\section{Lead's Meetings}
\label{leads}

\begin{enumerate}
\item The President shall schedule a minimum of two Leads’ meetings per month during the school
year. 
\item An agenda of a meeting must be made public to REV members at least eight hours before
the meeting. 
\item Official meetings are scheduled General Body Meetings, or an announced emergency meeting.
\item Meeting quorum shall consist of two-thirds of the Leadership. These members are hereon referred to as "voting members".
\item Meetings shall normally be open to the entire REV community. 
\item The President may request removal of any person who is disrupting the meeting. 
\item Robert's Rules of Order shall be referenced to cover any question on procedure or point of order
not covered in these by-laws. [Examples: http://www.robertsrules.org/]
\item Emergency meetings may be called by the President or by a two-thirds vote of Leadership; the President must notify at all REV General members
of the emergency meeting at least 24 hours in advance. 
\item A phone or email vote on a motion may only take place if: 
    \begin{enumerate}
    \item The motion is of an emergency nature or school is not in session. 
    \item The motion is considered to pass only if a majority of the current membership of the
cabinet vote in favor of the motion. 
    \item Each member receives the proposal prior to voting.
    \item The motion is reconsidered at the next official meeting. The phone motion may only be
made by the President.
    \end{enumerate}
\end{enumerate}

\subsection{Motions}
\label{leads:motions}

A Motion may be made at any time during a Lead's meeting by a voting member. For the Motion to be considered, it must be seconded by another voting member. Once the Motion is seconded, it will be voted on. For a Motion to pass, it must be approved by a simple majority of the present voting members.
