\section{Impeachment}
\label{impeachment}

\subsection{Disciplinary Action}
\label{impeachment:discipline}

\begin{enumerate}
\item Partial and total membership benefits and rights can be revoked by a majority vote of the voting members at a regular business meeting if a person has violated club rules or Union/Institute regulations.
\item At any time during the penalty period, the issue resulting in the withdrawal of membership rights may be appealed to the Team’s Adviser(s). The penalty remains in effect unless overturned by the Team’s Adviser(s).
\item A majority vote of those attending a General Body Meeting is needed to determine whether or not disciplinary action will be needed. The person in question has the right to speak before the vote is taken, but he or she must not be present when the vote is being taken.
\item Any regular member may make the motion to impeach an officer at a regular business meeting. After the discussion, the vote will be taken. If the motion to impeach the officer passes, the impeachment vote will be taken at the next regular business meeting in the manner described above.
\item Any officer may resign at any time. If there is an officer vacancy, there will be an orderly movement up the chain of succession unless an officer does not want to change positions or if there are no officer(s) to fill the vacancy(s). The empty seats(s) may be filled by appointment of the President or general election, depending on a majority vote at a regular business meeting. 
\end{enumerate}

\subsection{Succession of Leadership}
\label{impeachment:succession}

When a Leadership position is vacated, either from impeachment or resignation, the new role will be filed as follows. If the vacated role is filled by another member of Leadership, these rules should be followed for filling the newly vacated spot. Note that the apointee should be able to fill all requirements laid out in Section \ref{roles:qualifications}.

\subsubsection{President}
\label{impeachment:succession:president}

When the President leaves office, the current Vice President should fill that role.

\subsubsection{Vice President}
\label{impeachment:succession:vice}

When the Vice President leaves office, the new Vice President should be appointed by both the Project Manager and President.

\subsubsection{Project Manager}
\label{impeachment:succession:pm}

When the Project Manager leaves office, the new Project Manager should be a Lead appointed by the President.

\subsubsection{Lead}
\label{impeachment:succession:lead}

When a Lead vacates their position, the Assistant Lead from the respective System should fill that role. If they decline, a new Lead may be appointed from that System by the Project Manager.

\subsubsection{Assistant Lead}
\label{impeachment:succession:assistant}

When an Assistant Lead leaves office, the Lead for the respective System should appoint a new Assistant Lead with the approval of the Project Manager.