\section{Team Roles \& Election Process}
\label{roles}
The Officer roles are
\begin{itemize}
\item President
\item Vice President
\item Project Manager
\end{itemize}

\subsection{Election Process}
\label{roles:process}
\begin{enumerate}
\item The annual election and appointment of officers shall be held five weeks before the end of Spring semester at a General Body Meeting
    \begin{enumerate}
    \item  In the event that the Team's competition interferes with the election, by motion passed by Leadership, the election shall be scheduled two weeks after the competition.
    \end{enumerate}
\item The GBM in which elections are being held must have time allocated before the vote to allow Candidate running to present a speech with a maximum length of five minutes. Candidates will speak in alphabetical order.
\item After all Members wishing to run have spoken, the floor will be open for general discussion and questions directed towards those running.
\item After all candidates have spoken, any Member may speak about the Candidates for a maximum of two minutes.
\item The vote for each position is taken by Members writing down whom they wish to vote for and the position to elect them to on a sheet of paper. The President collects these papers and tallies the votes. If a tie exists between candidates who receive the most votes, the candidates that are not tied will be dropped from the ballot. The remaining candidates will have another chance to briefly talk, then a re-vote will be taken. If a tie persists, a coin flip will break the tie. 
\item Two General Body Meetings before the election, all REV Members will be informed by the President, via email, of
    \begin{enumerate}
    \item The positions available to be run for
    \item A description and the responsibilities of each position
    \item The requirements for candidacy of the position
    \item The date, time, and place the election will be held
    \end{enumerate}
\item If there is only one candidate running for a position, a simple majority will be required for the candidate to be elected into office.
    \begin{enumerate}
    \item  If a simple majority is not met, the eligible Members will be notified that they have the ability to run for the position.
    \item During the next week candidates will be collected and then the election for the contested position proceeds as normal at the next GBM
    \item If no volunteers appear the candidate must receive at least one vote in order to take office
    \item If no votes exist for the candidate the newly elected policy makers should appoint the successor. If there are no new policy makers, the previous holder of the contested position may appoint their successor
    \end{enumerate}
\item In the event that a candidate cannot make the election, they may record a video with a statement to be shown at that election. They may field questions by phone.
\item There is no proxy voting for an election.
\end{enumerate}

\subsection{Appointed Positions}
\label{roles:appointed}

\subsubsection{Leads \& Systems}
\label{roles:appointed:leads}
After the annual election have been resolved, the Project Manager may then decide upon the structure of the rest of the team, with the approval of the President. The team shall be divided into Systems, each System led by a Lead. The rest of the Members in the club will be divided into the System of their choosing. The Project Manager may appoint any Member other than themselves or another Officer to the role of Lead, with the approval of the President. The title may be revoked at any point in time by the Project Manager with the approval of the President.

\subsubsection{Assistant Leads}
\label{roles:appointed:assistant}
After the Lead of each System has been appointed, the Lead may appoint an Assistant Lead to the System as second in command to the System. The Assistant Lead appointee must be approved by the Project Manager.

\subsection{Minimum Qualifications}
\label{roles:qualifications}

\subsubsection{President}
\label{roles:qualifications:president}
\begin{enumerate}
\item Be a Member of REV for at least 2 REV semesters.
\item Have held an Leadership position within the team for at least 1 of the previous 3 REV semesters.
\end{enumerate}

\subsubsection{Vice President}
\label{roles:qualifications:vice}
\begin{enumerate}
\item Be a Member of REV for at least 2 REV semesters.
\end{enumerate}

\subsubsection{Project Manager}
\label{roles:qualifications:pm}
\begin{enumerate}
\item Be a Member of REV for at least 2 REV semesters.
\item Have held a Leadership position within the team for at least 1 of the previous 3 REV semesters.
\end{enumerate}

\subsection{Responsibilities}
\label{roles:responsibilities}

\subsubsection{Leadership}
\label{roles:responsibilities:leadership}

It is expected that all Leadership behave in accordance with the intent and purpose of this organization. All Leadership are subject to the same disciplinary rules, regulations, and procedures as non-office-holding members.

\subsubsection{President}
\label{roles:responsibilities:president}

The President is foremost the driving force behind REV. They should manage the finances, corporate contacts, and all REV executive business, 
such as team meetings. The President should to the best of their ability carry out the purpose of REV. Works with the Project Manager 
for competition related decisions. The President may delegate some of this workload to the Vice President.

\subsubsection{Vice President}
\label{roles:responsibilities:vice}

The sole responsibility of the Vice President is to assist the President in performing his duties. The responsibilities will be determined by the President.

\subsubsection{Project Manager}
\label{roles:responsibilities:pm}

The Project Manager is the primary decision facilitator for all technical aspects and works with the President 
on competition related items. Their primary goal is to help oversee see the development of the club's projects.

\subsubsection{Lead}
\label{roles:responsibilities:lead}

A Lead should manage the System they are assigned and see it to completion. They are the primary contact to Leadership for many members, 
and should accurately reflect the needs of their System to the Officers.

\subsubsection{Assistant Lead}
\label{roles:responsibilities:assistant}

The sole responsibility of an Assistant Lead is to assist the respective Lead in performing their duties. The responsibilities will be determined by the respective Lead.