\section{Team Roles \& Election Process}
\label{roles}
The current Officer roles are
\begin{itemize}
\item President
\item Project Manager
\end{itemize}
The election process for the roles of Officers. The reasoning behind these roles as elected positions is that these are the primary policy makers of the team. The graduating seniors may not vote for these positions, but if the current President is running for office and cannot hold the vote then one of the graduating seniors can hold the election.

\subsection{Election Process}
\label{roles:process}
\begin{enumerate}
\item The annual election for Officers will be held on the third GBM after the Shell Eco-marathon, regardless of if the team competes or not.
\item The GBM in which elections are being held must have time allocated before the vote to allow any Member wishing to run for any position, and is qualified for that position, present a speech with a maximum length of five minutes. Candidates will speak in alphabetical order.
\item After all Members wishing to run have spoken, the floor will be open for general discussion and questions directed towards those running.
\item The vote for each position is taken by Members writing down whom they wish to vote for and the position to elect them to on a sheet of paper. The President collects these papers and tallies the votes. If a tie exists between candidates who receive the most votes, the candidates that are not tied will be dropped from the ballot. The remaining candidates will have another chance to briefly talk, then a re-vote will be taken. If a tie persists, Kristin Sechrest will be permitted to cast a vote to break the tie.
\item Two General Body Meetings before the election, all REV General Members will be informed by the President, via email, of
    \begin{enumerate}
    \item The positions available to be run for
    \item A description and the responsibilities of each position
    \item The requirements for candidacy of the position
    \item The date, time, and place the election will be held
    \end{enumerate}
\item If there is only one candidate running for a position, a simple majority will be required for the candidate to be elected into office.
    \begin{enumerate}
    \item  If a simple majority is not met, the eligible Members will be notified that they have the ability to run for the position.
    \item During the next week candidates will be collected and then the election for the contested position proceeds as normal at the next GBM
    \item If no volunteers appear the candidate must receive at least one vote in order to take office
    \item If no votes exist for the candidate the newly elected policy makers should appoint the successor. If there are no new policy makers, the previous holder of the contested position may appoint their successor
    \end{enumerate}
\end{enumerate}

\subsection{Appointed Positions}
\label{roles:appointed}

\subsubsection{Leads \& Systems}
\label{roles:appointed:leads}
After the annual election have been resolved, the Project Manager may then decide upon the structure of the rest of the team. The team shall be divided into Systems, each System led by a Lead. The rest of the Members in the club will be divided into the System of their choosing. The Project Manager may appoint any Member other than themselves or another Officer to the role of Lead. The title may be revoked at any point in time by the Project Manager.

\subsubsection{Assistant Leads}
\label{roles:appointed:assistant}
After the Lead of each System has been appointed, the Lead may appoint an Assistant Lead to the System as second in command to the System. The Assistant Lead appointee must be approved by the Project Manager.

\subsection{Minimum Qualifications}
\label{roles:qualifications}

\subsubsection{President}
\label{roles:qualifications:president}
\begin{enumerate}
\item Be a Member of REV for at least 2 REV semesters.
\item Have held an Officer or Lead position within the team for at least 1 of the previous 3 REV semesters.
\end{enumerate}

\subsubsection{Project Manager}
\label{roles:qualifications:pm}
\begin{enumerate}
\item Be a Member of REV for at least 2 REV semesters.
\item Have held a Lead or Assistant Lead position within the team for at least 1 of the previous 3 REV semesters.
\end{enumerate}

\subsection{Responsibilities}
\label{roles:responsibilities}

\subsubsection{President}
\label{roles:responsibilities:president}

\subsubsection{Project Manager}
\label{roles:responsibilities:pm}

\subsubsection{Lead}
\label{roles:responsibilities:lead}

\subsubsection{Assistant Lead}
\label{roles:responsibilities:assistant}
