\section{Proposals}
\label{proposals}
\begin{enumerate}
\item To be considered for floor time at a Leads’ Meeting, a proposal must have:
    \begin{enumerate}
    \item Justification for the Project and Part(s) in relation to Team resources and a Plan of
Implementation amongst the relevant subsystem(s)
    \item Technical approval from a relevant professional or professor-verified in the form of a
dated signature. 
        \begin{enumerate}
        \item Technical signatures may be omitted if items are found on and meet them requirements in Appendix \ref{allowed_items}
        \item Appendix \ref{allowed_items} will be approved and modified by a Leads’ Meeting vote, contingent on Advisor approval
        \end{enumerate}
    \item A proposed plan of purchasing including 
        \begin{enumerate}
        \item Method(s) of purchasing for each item
        \item  Source(s) of funding (either internal or external) [i.e. Specific accounts and budgets, sponsors/donors]
        \item Any impacts on or deviations from previous purchasing plans
        \end{enumerate}
    \end{enumerate}
\item All items in the above item 1 must be submitted in writing to the President no later than 4pm the day before the scheduled Leads’ Meeting. Face-to-face conversation is encouraged, relevant Team members and others should be consulted before submitting a proposal.
\item Any REV Team member in good standing may submit a proposal. 
    \begin{enumerate}
    \item The individual who submits a proposal will be, by default, asked to present it at the Leads’ meeting where it is scheduled to be presented
    \item Should the Team member who submitted the proposal not wish to present it, he may designate someone to present on his behalf, the designee must agree and confirm his intent to present. 
    \end{enumerate}
\item The President has the right to refuse any proposals that are incomplete, obscene, irrelevant.
    \begin{enumerate}
    \item The President must notify all Leads and Officers of the submitted proposal and the reason for denial. 
    \item If an upcoming meeting does not have time to allow for discussion and voting on the proposal, the President may wait until the next available meeting time to schedule the proposal, should this occur, the president must notify the presenter immediately. 
    \end{enumerate}
\item All approved proposals will be given discussion time at a Leads’ meeting. This time will be used to allow for a presentation and explanation of the proposal. Questions are encouraged from all members present at the meeting.
\item Before a vote can take place, a motion must be written regarding the proposal. 
    \begin{enumerate}
    \item This motion must be created from a present voting member
    \item The motion must then be seconded by a second present voting member
    \item The Presenter of a proposal may not create or second a motion with regards to his proposal
    \end{enumerate}
\item Regardless of outcome, after a vote takes place on the proposal (as outlined in Section \ref{voting}) the motion and any supporting documentation must be documented and made accessible to all General REV members within 24 hours of the close of the Leads’ meeting. 
\end{enumerate}